Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 experiment_and_data.tex
new references included

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ackerstaff1998} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{2001}. The procedure used to select events is identical to that used in Ref.~\cite{2009a}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Burnsth2010,Zeiler2009} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

@@

An ``exclusive'' event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon that mediates the lepton-proton scattering process, $p$ is the four-momentum of the target proton and $q'$ is the four momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{2009a}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Burnsth2010}.

@@

A maximum-likelihood fitting technique \cite{Barlow1990} was used to
extract the asymmetry amplitudes in \blue{each} kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
This method, described in Ref.~\cite{HERMESCollaboration2008}, fits the expected
\blue{azimuthal} distribution function to the data without introducing binning effects in $\phi$.
Weights are introduced per event in the fitting procedure to account for
luminosity imbalances with respect to the beam charge and polarisation.

@@

At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Belitsky2002} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, \blue{in this} approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, whereas the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & $n$ = 2\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $n$ = 3\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3& $n$
= 3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $n$ = 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $n$ = 2, $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Belitsky2002}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is identical to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

@@

An ``exclusive'' event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon that mediates the lepton-proton scattering process, $p$ is the four-momentum of the target proton and $q'$ is the four momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Bur10}.

@@

A maximum-likelihood fitting technique \cite{Bar90} was used to
extract the asymmetry amplitudes in \blue{each} kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
This method, described in Ref.~\cite{Air08}, fits the expected
\blue{azimuthal} distribution function to the data without introducing binning effects in $\phi$.
Weights are introduced per event in the fitting procedure to account for
luminosity imbalances with respect to the beam charge and polarisation.

@@

At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, \blue{in this} approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, whereas the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & $n$ = 2\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $n$ = 3\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3& $n$
= 3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $n$ = 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $n$ = 2, $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}
